### 2021-05-29 ms/ms.tex
Final edits before acceptance

where $p_{r,t,a}$ is the proportion of annual returns in river $r$, year $t$,
and of spawning history $a$ (either 1SW or 2SW returns); $n_{r,t,s,a}$ is the
number of samples in river $r$, year $t$, of returning age $a$, and of size
group $s$; $n_{r,t,s}$ is the total number of samples in river $r$, year $t$,
and of size group $s$; and $N_{r,t,s}$ is the returns of salmon
in river $r$, year $t$, and of size group $s$.
For years where scale data of a given size group is lacking,
we averaged the proportions of annual returns
for the closest ten years for which there was data.
We incorporated the uncertainty in the conversion between
size group and returning age in the model indirectly as an estimate
of the variance of annual log-1SW and 2SW return abundance (see Supplementary Materials).

@@

We developed a hierarchical Bayesian model that uses Murphy's maturity
schedule method, in conjunction with informative priors, to estimate annual
marine survival in seven populations of Atlantic salmon. We account for
observation error in smolt and return estimates, as well as estimating the
proportion returning after one winter (i.e. \Pg) hierarchically.
There is an identifiability problem in the maturity schedule equations where
the parameter estimates cannot be optimally solved \citep{Chaput2003a}.
However, this issue can be mathematically overcome by
using informative priors for the two marine survival parameters and the maturation
parameter in a Bayesian framework.
This method requires abundance estimates of smolts as well as abundance estimates
of returning one-sea-winter (1SW) and two-sea-winter (2SW) adults. With these data,
it estimates three parameters: survival in the first year at sea (\So), survival
in the second year at sea (\St), and the proportion of fish returning after one
year at sea (\Pg).

@@

where $smolts_{true,r,t}$ are the true smolt abundances for river
$r$ and year $t$, and $\epsilon_{r,t}$ is the error term, which is calculated from the yearly
coefficient of variation in the empirically derived
smolt estimates (see Tables S4-6 in the Supplementary Material).
Where available, we used population-specific measurement error estimates for smolt abundances; if not
available, we set the measurement error at 5 or 10\%, depending on whether the smolt
abundance estimates originated from direct counts or mark-recapture studies, respectively
(see Table S5 in the Supplementary Material).
The log-transformed true smolt abundances are
normally distributed around a population-level mean and standard deviation:

@@

These priors, when converted to yearly survival, are roughly constrained between
0 and 0.2 for \So and between 0.2 and 0.5 for \St (Fig.~\ref{fig:priors}a). They are
informative only to the extent that they limit the estimates of marine survival
to what we considered to be biologically realistic based on previous studies on
return rates of 1SW-dominated populations in NL, as well as the couple studies
that have explored survival in the second winter at sea of Atlantic salmon in
eastern Canada.
Although two published values are higher than 0.8 \citep{Chaput2003b,Hubley2011}, most estimates of S2 encompass a range between 0.1 and 0.6; this is the empirical basis for our prior.
While there is circularity in setting priors based on data for the same rivers,
and is far from ideal, these are the only data we have available to set priors
and the models used previously are considerably different to the one in the present study.

@@

@@

Lastly, to determine what parameters best explains the number of returns in
the model (including the model uncertainty), we estimated the variance in returns explained by each parameter by
calculating the squared correlation between the estimated parameters and the
estimated 1SW and 2SW returns ($R_{1,r,t}$ and $R_{2,r,t+1}$ in
equations~\ref{eq:3} and~\ref{eq:4}).

@@

Roughly half (11) out of the 21 pair-wise correlations were significant (p-value below 0.05)
(Fig.~\ref{fig:s1-corr}). When looking at the direction of the correlations,
these spanned both positive and negative coefficients. All seven populations had both
positive and negative correlations among them.
The corrected pair-wise correlations in $Z_1$ were almost identical to the
uncorrected ones as the error variance and covariance terms were very small.
The correlations between populations in the region were positive between Nashwaak and LaHave (Scotia-Fundy region), non-significant between the Trinit\'{e} and Saint-Jean (QC),
non-significant between WAB and Campbellton but negative between Conne and WAB (NL).
The Campbellton had mostly non-significant pairwise correlations with other populations, even though there are both positive and negative correlation coefficients, except with the Saint-Jean
where the correlation between $Z_1$ trends is positive and significant.
Note that the uncertainty in these correlations reflect the uncertainty in the
measurements, but not in the process (in this respect they are equivalent to
population variance and not sample variance).
Our choice of priors affected these correlations:
using weaker priors for \So and \St resulted in slightly different coefficients and significance thresholds (see Fig. S7 of Supplementary materials).

\begin{figure}[htbp] \centering
    \includegraphics[width=0.95\linewidth]{figures/corrplot-post-z1-corrected.png} \caption{
        Correlations of estimated trends in $Z_1$ among populations.
        Correlation coefficients are shown in each square, while colouring
        denotes significance of the correlation ($p \leq 0.05$) as well as the direction and magnitude.}
\label{fig:s1-corr}
\end{figure}

@@

Our results show that trends in marine survival among monitored Atlantic salmon
populations in eastern Canada are highly variable, both temporally and
spatially. Over the time periods for which data were available, some
populations show positive trends in survival in the first winter at sea (\So)
while other exhibits highly variable yet stationary trends, and some show declines.
Variation in survival at the population level can be large even within a
region. With one possible exception (LaHave River), consistent declines in
marine survival within populations are not evident since the onset of fishing
moratoria.

@@

Thirdly, the accuracy and precision of the model's output is different
for different populations. Survival in the first year at sea is the variable
that explains most of the variance in estimates of 1SW returns, except for the
Saint-Jean; it seems
the model does not provide reliable parameter estimates for this population,
which is the population with the highest proportion of 2SW returns.
Furthermore, estimates of \St and \Pg in all populations are negatively correlated and highly
uncertain, and this must be considered when making any inferences based on
these parameters for any of the populations examined.

@@

@@

We would like to thank Martha Robertson, G\'{e}rald Chaput, and Carmen David
their useful comments on the manuscript, and Sean Anderson for his help with
implementing the non-centered parameterization of the model. Hydro-Québec
contributed to data acquisition from Rivière de la Trinité. This research was
supported by the Atlantic Salmon Conservation Foundation and the Atlantic
Salmon Research Joint Venture.
GHB was funded by the Norwegian Research Council (project 275862 and 280308).

>>>>

where $p_{r,t,a}$ is the proportion of annual returns in river $r$, year $t$,
and of spawning history $a$ (either 1SW or 2SW returns); $n_{r,t,s,a}$ is the
number of samples in river $r$, year $t$, of returning age $a$, and of size
group $s$; $n_{r,t,s}$ is the total number of samples in river $r$, year $t$,
and of size group $s$; and $N_{r,t,s}$ is the returns of salmon
in river $r$, year $t$, and of size group $s$.
For years where scale data of a given size group is lacking,
we averaged the proportions of annual returns
for the closest ten years for which there were data.
We incorporated the uncertainty in the conversion between
size group and returning age in the model indirectly as an estimate
of the variance of annual log-1SW and 2SW return abundance (see Supplementary Materials).

@@

We developed a hierarchical Bayesian model that uses Murphy's maturity
schedule method, in conjunction with informative priors, to estimate annual
marine survival. We account for
observation error in smolt and return estimates, as well as estimating the
proportion returning after one winter (i.e. \Pg) hierarchically.
There is an identifiability problem in the maturity schedule equations where
the parameter estimates cannot be optimally solved \citep{Chaput2003a}.
However, this issue can be mathematically overcome by
using informative priors for the two marine survival parameters and the maturation
parameter in a Bayesian framework.
This method requires abundance estimates of smolts as well as abundance estimates
of returning one-sea-winter (1SW) and two-sea-winter (2SW) adults. With these data,
it estimates three parameters: survival in the first year at sea (\So), survival
in the second year at sea (\St), and the proportion of fish returning after one
year at sea (\Pg).

@@

where $smolts_{true,r,t}$ are the true smolt abundances for river
$r$ and year $t$, and $\epsilon_{r,t}$ is the error term, which is calculated from the yearly
coefficient of variation in the empirically derived
smolt estimates (see Tables S4-6 in the Supplementary Materials).
Where available, we used population-specific measurement error estimates for smolt abundances; if not
available, we set the measurement error at 5 or 10\%, depending on whether the smolt
abundance estimates originated from direct counts or mark-recapture studies, respectively
(see Table S5 in the Supplementary Materials).
The log-transformed true smolt abundances are
normally distributed around a population-level mean and standard deviation:

@@

These priors, when converted to yearly survival, are roughly constrained between
0 and 0.2 for \So and between 0.2 and 0.5 for \St (Fig.~\ref{fig:priors}a). They are
informative only to the extent that they limit the estimates of marine survival
to what we considered to be biologically realistic based on previous studies on
return rates of 1SW-dominated populations in NL, as well as the few studies
that have explored survival in the second winter at sea of Atlantic salmon in
eastern Canada.
Although two published values are higher than 0.8 \citep{Chaput2003b,Hubley2011}, most estimates of S2 encompass a range between 0.1 and 0.6; this is the empirical basis for our prior.
While there is circularity in setting priors based on data for the same rivers,
and is far from ideal, these are the only data we have available to set priors
and the models used previously are considerably different to the one in the present study.

@@

We explored the effect of using weaker priors for $Z_1$, $Z_2$ and \Pg, and found
that the posteriors of $Z_1$ were not sensitive to the choice of prior, while the 
 posteriors $Z_2$ and \Pg became more uncertain with weaker priors while maintaining
 the same temporal trends observed when using stronger priors. See Figs S2-7 in the Supplementary Materials.

@@

Lastly, to determine which parameters best explain the number of returns in
the model (including the model uncertainty), we estimated the variance in returns explained by each parameter by
calculating the squared correlation between the estimated parameters and the
estimated 1SW and 2SW returns ($R_{1,r,t}$ and $R_{2,r,t+1}$ in
equations~\ref{eq:3} and~\ref{eq:4}).

@@

Roughly half (11) out of the 21 pair-wise correlations were significant (p-value below 0.05)
(Fig.~\ref{fig:s1-corr}). When looking at the direction of the correlations,
these spanned both positive and negative coefficients. All seven populations had both
positive and negative correlations among them.
The corrected pair-wise correlations in $Z_1$ were almost identical to the
uncorrected ones as the error variance and covariance terms were very small.
The correlations between populations in the region were positive between Nashwaak and LaHave (Scotia-Fundy region), non-significant between the Trinit\'{e} and Saint-Jean (QC),
non-significant between WAB and Campbellton but negative between Conne and WAB (NL).
Campbellton had mostly non-significant pairwise correlations with other populations, even though there are both positive and negative correlation coefficients, except with the Saint-Jean
where the correlation between $Z_1$ trends is positive and significant.
Note that the uncertainty in these correlations reflect the uncertainty in the
measurements, but not in the process (in this respect they are equivalent to
population variance and not sample variance).
Our choice of priors affected these correlations:
using weaker priors for \So and \St resulted in slightly different coefficients and significance thresholds (see Fig. S7 of Supplementary Materials).

\begin{figure}[htbp] \centering
    \includegraphics[width=0.95\linewidth]{figures/corrplot-post-z1-corrected.png} \caption{
        Correlations of estimated trends in instantaneous natural mortality in the first winter at sea, $Z_1$, among populations.
        Correlation coefficients are shown in each square, while colouring
        denotes significance of the correlation ($p \leq 0.05$) as well as the direction and magnitude.}
\label{fig:s1-corr}
\end{figure}

@@

Our results show that trends in marine survival among monitored Atlantic salmon
populations in eastern Canada are highly variable, both temporally and
spatially. Over the time periods for which data were available, some
populations show positive trends in survival in the first winter at sea (\So)
while others exhibit highly variable yet stationary trends, and some show declines.
Variation in survival at the population level can be large even within a
region. With one possible exception (LaHave River), consistent declines in
marine survival within populations are not evident since the onset of fishing
moratoria.

@@

Thirdly, the accuracy and precision of the model's output is different
for different populations. Survival in the first year at sea is the variable
that explains most of the variance in estimates of 1SW returns, except for the
Saint-Jean; it seems
the model does not provide reliable parameter estimates for this population,
which is the population with the highest proportion of 2SW returns.
Furthermore, estimates of \St and \Pg in all populations are negatively correlated and highly
uncertain, and this must be considered when making any inferences based on
these parameters for any of the populations examined, at least for those population appreciable contributions of 2SW salmon.

@@

\section*{Data Availability Statement}

The data and code underlying this article are available in GitHub, at \url{https://github.com/sebpardo/salmon-marine-survival}.

@@

We would like to thank Martha Robertson, G\'{e}rald Chaput, and Carmen David
their useful comments on the manuscript, and Sean Anderson for his help with
implementing the non-centered parameterization of the model. Hydro-Québec
contributed to data acquisition from Rivière de la Trinité. This research was
supported by the Atlantic Salmon Conservation Foundation and the Atlantic
Salmon Research Joint Venture.
GHB was funded by the Norwegian Research Council (projects 275862 and 280308).

### 2021-05-29 ms/suppmat.tex
Final edits before acceptance

The model runs with weaker priors did not differ mayorly from those with
stronger priors, particularly for posterior estimates of \So, which show the
same overall trends for all populations and some yearly \So estimates with
high uncertainty (i.e., large error bars) show greater uncertainty uncertainty
under the weak \So and \St scenario (Fig.~\ref{fig:s1-trends-priors}).
Not unexpectedly, the weak \Pg scenario had no visually discernible effect on
posterior estimates of \So.

@@

\begin{figure}[htbp] \centering
    \includegraphics[width=0.95\linewidth]{figures/corrplot-post-z1-corrected-weakz.png} \caption{
        Correlations of estimated trends in $Z_1$ among populations with weak \So and
\St priors. Correlation coefficients are shown in each square, while colouring
        denotes significance of the correlation ($p \leq 0.05$) as well as the direction and magnitude.}
\label{fig:s1-corr-weakz}
\end{figure}

>>>>

The model runs with weaker priors did not differ majorly from those with
stronger priors, particularly for posterior estimates of \So, which show the
same overall trends for all populations and some yearly \So estimates with
high uncertainty (i.e., large error bars) show greater uncertainty uncertainty
under the weak \So and \St scenario (Fig.~\ref{fig:s1-trends-priors}).
Not unexpectedly, the weak \Pg scenario had no visually discernible effect on
posterior estimates of \So.

@@

\begin{figure}[htbp] \centering
    \includegraphics[width=0.95\linewidth]{figures/corrplot-post-z1-corrected-weakz.png} \caption{
        Correlations of estimated trends in in instantaneous natural mortality in the first winter at sea, $Z_1$, among populations with weak \So and
\St priors. Correlation coefficients are shown in each square, while colouring
        denotes significance of the correlation ($p \leq 0.05$) as well as the direction and magnitude.}
\label{fig:s1-corr-weakz}
\end{figure}
